---
title: "MusicCharts.world"
subtitle: "A weekly exploration of how Spotify charts overlap across countries"
author: "chai publications"
description-meta: "An independent weekly exploration of Spotify chart overlap, movement, and local listening patterns across countries."
canonical-url: "https://musiccharts.world/"
output-file: index.html
open-graph: true
twitter-card: true
format:
  html:
    toc: false
    page-layout: full
    css: world-music-watch.css
    embed-resources: false
    code-tools: false
execute:
  echo: false
  warning: false
  message: false
---

```{=html}
<style>
.selected-flag {
  font-size: 2rem;
  vertical-align: middle;
  margin-right: 8px;
}
.playback-controls {
  display: flex;
  align-items: center;
  gap: 6px;
  flex-wrap: wrap;
  margin: 6px 0;
}
.queue-btn {
  background: #5a2616;
  color: #faf6ef;
  border: none;
  border-radius: 4px;
  padding: 5px 12px;
  font-size: 0.82rem;
  cursor: pointer;
  white-space: nowrap;
  transition: background 0.15s;
}
.queue-btn:hover {
  background: #c97a4f;
}
.queue-btn.stop {
  background: #8b3a2a;
}
.queue-btn.stop:hover {
  background: #b04a30;
}
.queue-indicator {
  font-size: 0.8rem;
  color: #c97a4f;
  font-weight: 600;
  margin-left: 6px;
}
</style>
```

```{r setup}
#| include: false
library(dplyr)
library(tidyr)
library(purrr)
library(stringr)
library(plotly)
library(htmltools)
library(htmlwidgets)
library(lubridate)

source("R/fetch_charts.R")

# Production uses the complete configured list. A deliberate environment
# override supports small local smoke renders without changing that list.
market_override <- trimws(Sys.getenv("MUSICCHARTS_TEST_MARKETS"))
if (nzchar(market_override)) {
  country_codes <- tolower(trimws(strsplit(market_override, ",", fixed = TRUE)[[1]]))
  unknown_markets <- setdiff(country_codes, WORLD_MUSIC_WATCH_COUNTRIES)
  if (length(unknown_markets) > 0L) {
    stop("Unknown MUSICCHARTS_TEST_MARKETS values: ", paste(unknown_markets, collapse = ", "))
  }
} else {
  country_codes <- WORLD_MUSIC_WATCH_COUNTRIES
}

# Convert ISO-2 country code to flag emoji via regional indicator symbols.
flag_emoji <- function(codes) {
  vapply(codes, function(code) {
    if (is.na(code) || code == "GLOBAL") return("\U0001F30D")
    pts <- utf8ToInt(toupper(code)) - utf8ToInt("A") + 0x1F1E6
    if (any(pts < 0x1F1E6) || any(pts > 0x1F1FF)) return("")
    intToUtf8(pts)
  }, character(1))
}

# Render a position-change cell from kworb's "P+" text
render_change <- function(ch) {
  if (is.na(ch) || ch == "") return('<span class="track-change blank"><span class="visually-hidden">Movement unavailable</span></span>')
  if (ch == "=")   return('<span class="track-change same"><span aria-hidden="true">&mdash;</span><span class="visually-hidden">No change</span></span>')
  if (ch == "NEW") return('<span class="track-change new"><span aria-hidden="true">NEW</span><span class="visually-hidden">New entry</span></span>')
  if (ch == "RE")  return('<span class="track-change re"><span aria-hidden="true">RE</span><span class="visually-hidden">Re-entry</span></span>')
  if (substr(ch, 1, 1) == "+") return(sprintf('<span class="track-change up"><span aria-hidden="true">&uarr;%s</span><span class="visually-hidden">Up %s positions</span></span>', substring(ch, 2), substring(ch, 2)))
  if (substr(ch, 1, 1) == "-") return(sprintf('<span class="track-change down"><span aria-hidden="true">&darr;%s</span><span class="visually-hidden">Down %s positions</span></span>', substring(ch, 2), substring(ch, 2)))
  sprintf('<span class="track-change">%s</span>', htmlEscape(ch))
}
```

```{r fetch}
#| include: false

validated_run_path <- trimws(Sys.getenv("MUSICCHARTS_VALIDATED_RUN"))
if (nzchar(validated_run_path)) {
  if (!file.exists(validated_run_path)) {
    stop("Validated chart snapshot does not exist: ", validated_run_path)
  }
  chart_run <- readRDS(validated_run_path)
  if (!identical(chart_run$validation_status, "pass")) {
    stop("The supplied chart snapshot did not pass critical validation.")
  }
  if (!identical(toupper(country_codes), chart_run$configured_markets)) {
    stop("The supplied chart snapshot does not match the configured market list.")
  }
} else {
  chart_run <- fetch_chart_run(country_codes, top_n = 50)
}
charts <- chart_run$charts
charts_global <- chart_run$charts_global
chart_period <- chart_run$chart_period
fetch_timestamp <- chart_run$fetched_at
coverage <- chart_run$coverage
git_commit <- Sys.getenv("GITHUB_SHA", unset = "local")
github_run_id <- Sys.getenv("GITHUB_RUN_ID", unset = "local")
github_run_url <- if (github_run_id == "local") {
  "local"
} else {
  paste0(
    Sys.getenv("GITHUB_SERVER_URL", unset = "https://github.com"), "/",
    Sys.getenv("GITHUB_REPOSITORY", unset = "local"), "/actions/runs/",
    github_run_id
  )
}
```

```{r metrics}
#| include: false

country_info <- tibble::tribble(
  ~country_code, ~iso3,  ~country,                ~language,
  "US", "USA",  "United States",         "en",   "GB", "GBR",  "United Kingdom",        "en",
  "CA", "CAN",  "Canada",                "en",   "AU", "AUS",  "Australia",             "en",
  "IE", "IRL",  "Ireland",               "en",   "NZ", "NZL",  "New Zealand",           "en",
  "BR", "BRA",  "Brazil",                "pt",   "PT", "PRT",  "Portugal",              "pt",
  "MX", "MEX",  "Mexico",                "es",   "AR", "ARG",  "Argentina",             "es",
  "CO", "COL",  "Colombia",              "es",   "ES", "ESP",  "Spain",                 "es",
  "CL", "CHL",  "Chile",                 "es",   "PE", "PER",  "Peru",                  "es",
  "EC", "ECU",  "Ecuador",               "es",   "UY", "URY",  "Uruguay",               "es",
  "PY", "PRY",  "Paraguay",              "es",   "BO", "BOL",  "Bolivia",               "es",
  "DO", "DOM",  "Dominican Republic",    "es",   "GT", "GTM",  "Guatemala",             "es",
  "CR", "CRI",  "Costa Rica",            "es",
  "DE", "DEU",  "Germany",               "de",   "AT", "AUT",  "Austria",               "de",
  "CH", "CHE",  "Switzerland",           "de",   "FR", "FRA",  "France",                "fr",
  "BE", "BEL",  "Belgium",               "fr",   "IT", "ITA",  "Italy",                 "it",
  "NL", "NLD",  "Netherlands",           "nl",   "SE", "SWE",  "Sweden",                "sv",
  "NO", "NOR",  "Norway",                "no",   "DK", "DNK",  "Denmark",               "da",
  "FI", "FIN",  "Finland",               "fi",   "PL", "POL",  "Poland",                "pl",
  "CZ", "CZE",  "Czechia",               "cs",   "HU", "HUN",  "Hungary",               "hu",
  "RO", "ROU",  "Romania",               "ro",   "TR", "TUR",  "Turkey",                "tr",
  "GR", "GRC",  "Greece",                "el",   "JP", "JPN",  "Japan",                 "ja",
  "KR", "KOR",  "South Korea",           "ko",   "TW", "TWN",  "Taiwan",                "zh",
  "HK", "HKG",  "Hong Kong",             "zh",   "ID", "IDN",  "Indonesia",             "id",
  "PH", "PHL",  "Philippines",           "fil",  "TH", "THA",  "Thailand",              "th",
  "VN", "VNM",  "Vietnam",               "vi",   "MY", "MYS",  "Malaysia",              "ms",
  "SG", "SGP",  "Singapore",             "en",   "IN", "IND",  "India",                 "hi",
  "ZA", "ZAF",  "South Africa",          "en",   "NG", "NGA",  "Nigeria",               "en",
  "AE", "ARE",  "United Arab Emirates",  "ar",   "SA", "SAU",  "Saudi Arabia",          "ar",
  "EG", "EGY",  "Egypt",                 "ar",   "IL", "ISR",  "Israel",                "he"
)

n_countries_tracked <- n_distinct(charts$country_code)

charts <- charts |> left_join(country_info, by = "country_code")

# --- distinctiveness via Jaccard distance over track IDs --------------------
by_country <- split(charts$track_id, charts$country_code)

jaccard_dist <- function(a, b) {
  a <- unique(a); b <- unique(b)
  if (length(a) == 0 || length(b) == 0) return(1)
  1 - length(intersect(a, b)) / length(union(a, b))
}

cc <- names(by_country)
n  <- length(cc)
dist_mat <- matrix(0, n, n, dimnames = list(cc, cc))
for (i in seq_len(n)) for (j in seq_len(n)) if (i < j) {
  d <- jaccard_dist(by_country[[i]], by_country[[j]])
  dist_mat[i, j] <- dist_mat[j, i] <- d
}

distinctiveness <- rowMeans(dist_mat)

track_country_count <- charts |> count(track_id, name = "n_countries")
unique_to_one  <- track_country_count |> filter(n_countries == 1) |> pull(track_id)

stats <- tibble(
  country_code = cc,
  distinctiveness = distinctiveness
) |>
  left_join(country_info, by = "country_code") |>
  arrange(desc(distinctiveness))

# Hierarchical clustering for the heatmap
hc <- hclust(as.dist(dist_mat), method = "average")
order_idx <- hc$order
cc_ordered <- cc[order_idx]
labels_ordered <- country_info$country[match(cc_ordered, country_info$country_code)]

sim_mat <- 1 - dist_mat[order_idx, order_idx]
diag(sim_mat) <- NA_real_

most_distinctive <- stats |> slice_max(distinctiveness, n = 1, with_ties = FALSE)
least_distinctive <- stats |> slice_min(distinctiveness, n = 1, with_ties = FALSE)
sim_pairs <- which(upper.tri(sim_mat) & !is.na(sim_mat), arr.ind = TRUE)
strongest_pair_idx <- sim_pairs[which.max(sim_mat[sim_pairs]), , drop = FALSE]
strongest_pair <- c(
  labels_ordered[strongest_pair_idx[1, 1]],
  labels_ordered[strongest_pair_idx[1, 2]]
)
strongest_pair_overlap <- sim_mat[strongest_pair_idx]
```

::: {.kicker}
Chart week ending `r paste(format(chart_period, "%B"), as.integer(format(chart_period, "%d")), format(chart_period, "%Y"))` · verified from source · fetched `r fetch_timestamp`
:::

## What the world is listening to, [and where it disagrees.]{.italic-rust}

::: {.standfirst}
MusicCharts.world is an independent weekly exploration of how Spotify charts overlap across countries. Rankings are sourced through Kworb, and the site is not affiliated with or endorsed by Spotify.
:::

::: {.panel-tabset}

## The charts

::: {.section-intro}
Click any country on the map &mdash; or pick from the dropdown &mdash; to see its top 50. Choose a track to play it. Use **Play All** to listen through the full chart in order, or **Shuffle** to randomise.

Coverage for this issue: `r coverage$successful_markets` of `r coverage$configured_markets` configured markets loaded; `r coverage$unavailable_markets` unavailable from the upstream source; `r coverage$failed_markets` failed. Failed validation blocks publication.
:::

```{r world-map}
plot_ly(
  type = "choropleth",
  locations    = stats$iso3,
  z            = stats$distinctiveness,
  locationmode = "ISO-3",
  customdata   = stats$country_code,
  text         = stats$country,
  hovertemplate = "<b>%{text}</b><br>Distinctiveness: %{z:.3f}<br><i>click to view chart</i><extra></extra>",
  colorscale   = list(c(0, "#f5e8d6"), c(0.5, "#c97a4f"), c(1, "#5a2616")),
  marker       = list(line = list(color = "#1a1410", width = 0.4)),
  colorbar     = list(title = list(text = "Distinctiveness", font = list(size = 11)),
                      thickness = 8, len = 0.5, tickformat = ".2f")
) |>
  layout(
    geo = list(showframe = FALSE, showcoastlines = FALSE,
               projection = list(type = "natural earth"),
               bgcolor = "#faf6ef", landcolor = "#ece5d8"),
    paper_bgcolor = "#faf6ef",
    margin = list(l = 0, r = 0, t = 8, b = 0),
    height = 480
  ) |>
  config(displayModeBar = FALSE) |>
  onRender("
    function(el, x) {
      el.on('plotly_click', function(data) {
        var code = data.points[0].customdata;
        if (!code) return;
        if (typeof showCountryPanel === 'function') showCountryPanel(code);
        var sel = document.getElementById('country-select');
        if (sel) sel.value = code;
        var bar = document.querySelector('.now-playing-bar');
        if (bar) bar.scrollIntoView({behavior: 'smooth', block: 'start'});
      });
    }
  ")
```

::: {.visual-summary}
Map summary: `r most_distinctive$country` has the highest distinctiveness score in this issue; `r least_distinctive$country` has the lowest. Distinctiveness is a site-generated comparison of current Top 50 overlap, not a Spotify metric.
:::

```{r charts-panels}
#| results: asis

selectable <- country_info |>
  filter(country_code %in% unique(charts$country_code)) |>
  arrange(country)

# --- Build the countryDefaults JS object (for player initialisation) -------
build_default <- function(cc, name, df) {
  list(cc = cc, name = name,
       trackId = df$track_id[1],
       title   = df$title[1],
       artist  = df$artist[1],
       flag    = flag_emoji(cc))
}

defaults <- list(build_default("GLOBAL", "Worldwide", charts_global))
for (i in seq_len(nrow(selectable))) {
  cc_i <- selectable$country_code[i]
  panel_data <- charts |> filter(country_code == cc_i) |> arrange(rank)
  if (nrow(panel_data) > 0) {
    defaults[[length(defaults) + 1]] <-
      build_default(cc_i, selectable$country[i], panel_data)
  }
}

esc_js <- function(s) {
  s <- gsub("\\\\", "\\\\\\\\", s)
  gsub('"', '\\\\"', s)
}

# --- Define handlers + countryDefaults BEFORE loading the iframe API -------
cat('<script>\n')
cat('const countryDefaults = {\n')
for (d in defaults) {
  cat(sprintf('  "%s": {trackId: "%s", name: "%s", title: "%s", artist: "%s", flag: "%s"},\n',
              d$cc, d$trackId,
              esc_js(d$name), esc_js(d$title), esc_js(d$artist), d$flag))
}
cat('};\n')

# Build trackQueues: mapping panel code to array of {trackId, title, artist}
cat('const trackQueues = {\n')
# Global queue
cat('  "GLOBAL": [\n')
for (i in seq_len(nrow(charts_global))) {
  cat(sprintf('    {trackId: "%s", title: "%s", artist: "%s"},\n',
              charts_global$track_id[i],
              esc_js(charts_global$title[i]),
              esc_js(charts_global$artist[i])))
}
cat('  ],\n')
# Country queues
for (i in seq_len(nrow(selectable))) {
  cc_i <- selectable$country_code[i]
  panel_data <- charts |> filter(country_code == cc_i) |> arrange(rank)
  if (nrow(panel_data) > 0) {
    cat(sprintf('  "%s": [\n', cc_i))
    for (j in seq_len(nrow(panel_data))) {
      cat(sprintf('    {trackId: "%s", title: "%s", artist: "%s"},\n',
                  panel_data$track_id[j],
                  esc_js(panel_data$title[j]),
                  esc_js(panel_data$artist[j])))
    }
    cat('  ],\n')
  }
}
cat('};\n')

cat('
let spotifyController = null;
let pendingPlayId = null;
let currentPanelCode = "GLOBAL";

// --- Queue state ---
let queueActive = false;
let queueOrder = [];
let queuePosition = -1;
let pollInterval = null;
let lastUpdateTime = 0;      // Date.now() of last playback_update
let lastKnownPos = 0;
let trackHasPlayed = false;   // true once we see pos > 0
let advancing = false;        // guard against double-advance

window.onSpotifyIframeApiReady = (IFrameAPI) => {
  const container = document.getElementById("spotify-player-container");
  if (!container) return;
  IFrameAPI.createController(container, {
    width: "100%",
    height: 80,
    uri: "spotify:track:" + countryDefaults.GLOBAL.trackId
  }, (ctrl) => {
    spotifyController = ctrl;

    // playback_update: just record state, the poll loop does decisions
    spotifyController.addListener("playback_update", (data) => {
      lastUpdateTime = Date.now();
      const pos = data.position || 0;
      if (!data.isPaused && pos > 0) {
        trackHasPlayed = true;
        lastKnownPos = pos;
      }
    });

    if (pendingPlayId) {
      spotifyController.loadUri("spotify:track:" + pendingPlayId);
      spotifyController.play();
      pendingPlayId = null;
    }
  });
};

// --- Poll loop: checks every second whether the track has ended ---
function startPoll() {
  stopPoll();
  pollInterval = setInterval(() => {
    if (!queueActive || advancing) return;
    const now = Date.now();
    const silenceMs = now - lastUpdateTime;
    // If the track played and then updates stopped for 3+ seconds,
    // the preview/track ended. Advance.
    if (trackHasPlayed && lastUpdateTime > 0 && silenceMs > 3000) {
      advancing = true;
      advanceQueue();
    }
  }, 1000);
}

function stopPoll() {
  if (pollInterval) { clearInterval(pollInterval); pollInterval = null; }
}

function showCountryPanel(code) {
  stopQueue();
  currentPanelCode = code;
  document.querySelectorAll(".country-panel").forEach(p => {
    p.style.display = (p.id === "panel-" + code) ? "block" : "none";
  });
  const def = countryDefaults[code];
  if (def && spotifyController) {
    spotifyController.loadUri("spotify:track:" + def.trackId);
  }
  const flagEl = document.getElementById("selected-flag");
  if (flagEl && def) flagEl.textContent = def.flag;
  const panel = document.getElementById("panel-" + code);
  if (panel) {
    panel.querySelectorAll(".track-row").forEach(r => {
      r.classList.remove("selected");
      r.setAttribute("aria-pressed", "false");
    });
    const first = panel.querySelector(".track-row");
    if (first) {
      first.classList.add("selected");
      first.setAttribute("aria-pressed", "true");
    }
  }
  const sel = document.getElementById("country-select");
  if (sel) sel.value = code;
}

function playTrack(panelCode, trackId, rank, rowEl) {
  stopQueue();
  if (spotifyController) {
    spotifyController.loadUri("spotify:track:" + trackId);
    spotifyController.play();
  } else {
    pendingPlayId = trackId;
  }
  const panel = document.getElementById("panel-" + panelCode);
  if (panel) {
    panel.querySelectorAll(".track-row").forEach(r => {
      r.classList.remove("selected");
      r.setAttribute("aria-pressed", "false");
    });
  }
  if (rowEl) {
    rowEl.classList.add("selected");
    rowEl.setAttribute("aria-pressed", "true");
  }
}

// --- Play All / Shuffle ---
function startQueue(shuffle) {
  const queue = trackQueues[currentPanelCode];
  if (!queue || queue.length === 0 || !spotifyController) return;
  queueOrder = Array.from({length: queue.length}, (_, i) => i);
  if (shuffle) {
    for (let i = queueOrder.length - 1; i > 0; i--) {
      const j = Math.floor(Math.random() * (i + 1));
      [queueOrder[i], queueOrder[j]] = [queueOrder[j], queueOrder[i]];
    }
  }
  queuePosition = 0;
  queueActive = true;
  advancing = false;
  startPoll();
  updateQueueUI();
  playQueueTrack();
}

function playQueueTrack() {
  const queue = trackQueues[currentPanelCode];
  if (!queue || queuePosition < 0 || queuePosition >= queueOrder.length) {
    stopQueue();
    return;
  }
  const idx = queueOrder[queuePosition];
  const track = queue[idx];
  // Reset tracking for the new track
  trackHasPlayed = false;
  lastKnownPos = 0;
  lastUpdateTime = Date.now();  // give it time to start
  advancing = false;
  spotifyController.loadUri("spotify:track:" + track.trackId);
  spotifyController.play();
  // Highlight the row
  const panel = document.getElementById("panel-" + currentPanelCode);
  if (panel) {
    const rows = panel.querySelectorAll(".track-row");
    rows.forEach(r => {
      r.classList.remove("selected");
      r.setAttribute("aria-pressed", "false");
    });
    if (rows[idx]) {
      rows[idx].classList.add("selected");
      rows[idx].setAttribute("aria-pressed", "true");
      rows[idx].scrollIntoView({behavior: "smooth", block: "nearest"});
    }
  }
  updateQueueUI();
}

function advanceQueue() {
  if (!queueActive) return;
  queuePosition++;
  if (queuePosition >= queueOrder.length) {
    stopQueue();
    return;
  }
  playQueueTrack();
}

function skipQueue() {
  if (queueActive) {
    advancing = true;
    advanceQueue();
  }
}

function stopQueue() {
  queueActive = false;
  queuePosition = -1;
  queueOrder = [];
  trackHasPlayed = false;
  lastKnownPos = 0;
  advancing = false;
  stopPoll();
  updateQueueUI();
}

function updateQueueUI() {
  const indicator = document.getElementById("queue-indicator");
  if (!indicator) return;
  if (queueActive) {
    const queue = trackQueues[currentPanelCode];
    const total = queueOrder.length;
    indicator.textContent = "Track " + (queuePosition + 1) + " of " + total;
    indicator.style.display = "inline";
  } else {
    indicator.style.display = "none";
  }
  const stopBtn = document.getElementById("queue-stop-btn");
  const skipBtn = document.getElementById("queue-skip-btn");
  if (stopBtn) stopBtn.style.display = queueActive ? "inline-block" : "none";
  if (skipBtn) skipBtn.style.display = queueActive ? "inline-block" : "none";
}
')
cat('</script>\n')

# --- Sticky control bar: flag + dropdown + playback controls + player ------
cat('<div class="now-playing-bar"><div class="np-row">')

cat('<div class="country-selector-wrap">')
cat('<span id="selected-flag" class="selected-flag" aria-hidden="true">\U0001F30D</span>')
cat('<label for="country-select">Showing chart for:</label>')
cat('<select id="country-select" onchange="showCountryPanel(this.value)">')
cat('<option value="GLOBAL">&mdash; Worldwide &mdash;</option>')
for (i in seq_len(nrow(selectable))) {
  cat(sprintf('<option value="%s">%s</option>',
              selectable$country_code[i],
              htmlEscape(selectable$country[i])))
}
cat('</select>')
cat('</div>')

cat('<div class="playback-controls">')
cat('<button type="button" class="queue-btn" onclick="startQueue(false)" aria-label="Play all tracks in chart order">&#9654; Play All</button>')
cat('<button type="button" class="queue-btn" onclick="startQueue(true)" aria-label="Shuffle all tracks in this chart">&#128256; Shuffle</button>')
cat('<button type="button" class="queue-btn" id="queue-skip-btn" onclick="skipQueue()" aria-label="Play next track" style="display:none;">&#9197; Next</button>')
cat('<button type="button" class="queue-btn stop" id="queue-stop-btn" onclick="stopQueue()" aria-label="Stop playback queue" style="display:none;">&#9632; Stop</button>')
cat('<span id="queue-indicator" class="queue-indicator" role="status" aria-live="polite" style="display:none;"></span>')
cat('</div>')

cat('<div id="spotify-player-container"></div>')

cat('</div></div>')

# --- Render all chart panels (track lists only) ----------------------------
render_chart_panel <- function(df, panel_code) {
  if (nrow(df) == 0) return("")
  out <- '<ol class="track-list">\n'
  for (i in seq_len(nrow(df))) {
    out <- paste0(out, sprintf(
      '<li class="track-list-item"><button type="button" class="track-row%s" onclick="playTrack(\'%s\', \'%s\', %d, this)" aria-pressed="%s" aria-label="Play rank %d: %s by %s"><span class="track-rank">%02d</span>%s<span class="track-meta"><span class="track-title">%s</span><span class="track-artist">%s</span></span></button></li>\n',
      if (i == 1) " selected" else "",
      panel_code,
      df$track_id[i],
      df$rank[i],
      if (i == 1) "true" else "false",
      df$rank[i],
      escape_chart_text(df$title[i], attribute = TRUE),
      escape_chart_text(df$artist[i], attribute = TRUE),
      df$rank[i],
      render_change(df$change[i]),
      escape_chart_text(df$title[i]),
      escape_chart_text(df$artist[i])
    ))
  }
  paste0(out, '</ol>\n')
}

cat('<div class="country-panel" id="panel-GLOBAL" style="display:block;">')
cat(render_chart_panel(charts_global, "GLOBAL"))
cat('</div>')

for (i in seq_len(nrow(selectable))) {
  cc_i <- selectable$country_code[i]
  panel_data <- charts |> filter(country_code == cc_i) |> arrange(rank)
  cat(sprintf('<div class="country-panel" id="panel-%s" style="display:none;">', cc_i))
  cat(render_chart_panel(panel_data, cc_i))
  cat('</div>')
}

# --- Load the Spotify iframe API last (handlers already defined) -----------
cat('<script src="https://open.spotify.com/embed/iframe-api/v1" async></script>\n')
```

## The wider view

::: {.section-intro}
Each country's top 50 is compared against every other country's. The matrix below is the *overlap* (Jaccard similarity) between every pair of charts, with countries reordered by hierarchical clustering &mdash; so linguistic and cultural blocs sit as visible squares on the diagonal.
:::

```{r heatmap}
plot_ly(
  z = sim_mat,
  x = labels_ordered,
  y = labels_ordered,
  type = "heatmap",
  colorscale = list(
    c(0,    "#faf6ef"),
    c(0.25, "#e8d4b8"),
    c(0.6,  "#c97a4f"),
    c(1,    "#5a2616")
  ),
  hovertemplate = "<b>%{y}</b> \u2194 <b>%{x}</b><br>Chart overlap: %{z:.0%}<extra></extra>",
  showscale = TRUE,
  colorbar = list(
    title = list(text = "Overlap", font = list(size = 11)),
    thickness = 8, len = 0.6, tickformat = ".0%"
  ),
  xgap = 1, ygap = 1
) |>
  layout(
    paper_bgcolor = "#faf6ef",
    plot_bgcolor  = "#faf6ef",
    xaxis = list(tickangle = -45, tickfont = list(size = 9),
                 showgrid = FALSE, zeroline = FALSE),
    yaxis = list(autorange = "reversed", tickfont = list(size = 9),
                 showgrid = FALSE, zeroline = FALSE),
    margin = list(l = 140, r = 20, t = 20, b = 140),
    height = 820
  ) |>
  config(displayModeBar = FALSE)
```

::: {.visual-summary}
Heatmap summary: `r strongest_pair[1]` and `r strongest_pair[2]` have the highest pairwise chart overlap in this issue (`r sprintf("%.0f%%", strongest_pair_overlap * 100)`). The complete matrix remains available above for exploration.
:::

### § 01 &mdash; What everyone is hearing

The tracks holding top-50 positions in the largest number of countries this week, out of the `r n_countries_tracked` national charts we track. The rest of the chart is cosmopolitan disagreement; these are the points of consensus.

```{r ubiquity}
#| results: asis

track_summary <- charts |>
  group_by(track_id) |>
  summarise(
    title       = first(title),
    artist      = first(artist),
    track_url   = first(track_url),
    n_countries = n_distinct(country_code),
    avg_rank    = mean(rank),
    best_rank   = min(rank),
    best_cc     = country_code[which.min(rank)],
    best_country = country[which.min(rank)],
    .groups = "drop"
  ) |>
  arrange(desc(n_countries), avg_rank) |>
  head(12)

cat('<div class="outlier-grid">\n')
for (i in seq_len(nrow(track_summary))) {
  cat(sprintf(
    '<article class="outlier"><div class="outlier-rank">%s in %d countries &middot; avg #%.0f</div><h3 class="outlier-title">%s</h3><p class="outlier-artist">%s</p><div class="outlier-player"><iframe title="Play %s by %s on Spotify" src="https://open.spotify.com/embed/track/%s?utm_source=generator&theme=0" width="100%%" height="80" frameborder="0" allow="autoplay; clipboard-write; encrypted-media; picture-in-picture" loading="lazy"></iframe></div></article>\n',
    flag_emoji(track_summary$best_cc[i]),
    track_summary$n_countries[i],
    track_summary$avg_rank[i],
    escape_chart_text(track_summary$title[i]),
    escape_chart_text(track_summary$artist[i]),
    escape_chart_text(track_summary$title[i], attribute = TRUE),
    escape_chart_text(track_summary$artist[i], attribute = TRUE),
    track_summary$track_id[i]
  ))
}
cat('</div>\n')
```

### § 02 &mdash; The week's biggest gainers

Tracks climbing the charts hardest right now: the cumulative number of positions gained across all countries where they're moving up. Velocity, not absolute popularity.

```{r gainers}
#| results: asis

gainers <- charts |>
  filter(!is.na(change), str_detect(change, "^\\+\\d")) |>
  mutate(positions_gained = as.integer(str_replace(change, "\\+", ""))) |>
  group_by(track_id) |>
  summarise(
    title       = first(title),
    artist      = first(artist),
    track_url   = first(track_url),
    n_countries = n_distinct(country_code),
    total_gain  = sum(positions_gained, na.rm = TRUE),
    best_rank   = min(rank),
    .groups = "drop"
  ) |>
  arrange(desc(total_gain), desc(n_countries)) |>
  head(12)

if (nrow(gainers) == 0) {
  cat('<p class="data-pending">Position-change data not yet captured for this snapshot. The next fresh fetch will populate this section.</p>\n')
} else {
  cat('<div class="outlier-grid">\n')
  for (i in seq_len(nrow(gainers))) {
    cat(sprintf(
      '<article class="outlier"><div class="outlier-rank">&uarr;%d places across %d countries</div><h3 class="outlier-title">%s</h3><p class="outlier-artist">%s</p><div class="outlier-player"><iframe title="Play %s by %s on Spotify" src="https://open.spotify.com/embed/track/%s?utm_source=generator&theme=0" width="100%%" height="80" frameborder="0" allow="autoplay; clipboard-write; encrypted-media; picture-in-picture" loading="lazy"></iframe></div></article>\n',
      gainers$total_gain[i],
      gainers$n_countries[i],
      escape_chart_text(gainers$title[i]),
      escape_chart_text(gainers$artist[i]),
      escape_chart_text(gainers$title[i], attribute = TRUE),
      escape_chart_text(gainers$artist[i], attribute = TRUE),
      gainers$track_id[i]
    ))
  }
  cat('</div>\n')
}
```

### § 03 &mdash; Songs the rest of the world hasn't heard

Each track here holds a top-50 position in exactly one country and appears nowhere else in our sample. The mirror image of § 01.

```{r outliers}
#| results: asis

outliers <- charts |>
  filter(track_id %in% unique_to_one) |>
  arrange(rank) |>
  group_by(country_code) |>
  slice_head(n = 1) |>
  ungroup() |>
  arrange(rank) |>
  head(12)

cat('<div class="outlier-grid">\n')
for (i in seq_len(nrow(outliers))) {
  cat(sprintf(
    '<article class="outlier"><div class="outlier-rank">%s &nbsp;#%02d in %s</div><h3 class="outlier-title">%s</h3><p class="outlier-artist">%s</p><div class="outlier-player"><iframe title="Play %s by %s on Spotify" src="https://open.spotify.com/embed/track/%s?utm_source=generator&theme=0" width="100%%" height="80" frameborder="0" allow="autoplay; clipboard-write; encrypted-media; picture-in-picture" loading="lazy"></iframe></div></article>\n',
    flag_emoji(outliers$country_code[i]),
    outliers$rank[i],
    htmlEscape(outliers$country[i]),
    escape_chart_text(outliers$title[i]),
    escape_chart_text(outliers$artist[i]),
    escape_chart_text(outliers$title[i], attribute = TRUE),
    escape_chart_text(outliers$artist[i], attribute = TRUE),
    outliers$track_id[i]
  ))
}
cat('</div>\n')
```

:::

## Coverage and availability

This issue uses the verified weekly chart period ending `r format(chart_period, "%d %B %Y")`. `r coverage$successful_markets` of `r coverage$configured_markets` configured national markets loaded successfully. The worldwide chart is validated separately.

`r if (length(chart_run$unavailable_markets) == 0) "No configured markets were unavailable from the upstream source for this issue." else paste("Unavailable markets:", paste(country_info$country[match(chart_run$unavailable_markets, country_info$country_code)], collapse = ", "), ".")`

The fetch completed at `r fetch_timestamp`. A source or parser failure is not silently omitted: it stops publication. An upstream 404 is reported here as unavailable and is not treated as a chart with zero entries.

**Publication metadata.** Chart period: `r as.character(chart_period)`. Data fetched at: `r fetch_timestamp`. Site deployed at: [pending deployment]{#site-deployed-at}. Git commit: `r git_commit`. GitHub Actions run: `r if (github_run_url == "local") github_run_id else paste0("[", github_run_id, "](", github_run_url, ")")`.

::: {.footer-note}
**Method.** Similarity, overlap, movement totals, and distinctiveness are analytical measures generated by MusicCharts.world from the current Top 50 snapshot. Distinctiveness is the mean Jaccard distance between a country's track-ID set and every other country's set. The heatmap shows the inverse &mdash; chart overlap &mdash; with countries reordered by hierarchical clustering (average linkage).

**Source and positioning.** Rankings are sourced through [Kworb](https://kworb.net/spotify/), which identifies Spotify Charts as its source. MusicCharts.world is independent and is not affiliated with or endorsed by Spotify. The verified chart period comes from the upstream weekly page; the fetch timestamp is recorded separately. Chart availability depends on that upstream source.

**Identity and limitations.** Spotify track IDs are source identifiers, not guaranteed canonical recording identities. Remasters, reissues, alternate versions, or replacement IDs may be treated separately, while catalog changes may interrupt continuity. Spotify penetration varies by country, and local panels can contain false positives where a track sits just outside the Top 50 elsewhere. Featured-artist text follows the upstream presentation and is not a complete credit record.
:::
